Supporting Information : Asymmetric tail association in extreme climatic events affects population-extinction risk

### 2019-10-15 SuppMat.Rmd
edited maintext

>>>>

<!--needs editing, I just dumped old text here-->
Copula, a rank based measure of association, is much more informative 
than linear correlation measure and a widely applied tool in dependence 
modeling [@joe2014_dependence; @nelsen2006_copula]. Copulas separate 
the information content of a bivariate dataset,
$(x_n, y_n)$ for $n = 1 \ldots N$, into two non-overlapping parts: the information in the marginal 
distributions (which is not about the association between the variables) and the rest of 
the information (which is solely about the association). The association information is revealed by 
the copula plot ($v_n$ against $u_n$) of the raw variables ($y_n$ vs. $x_n$) in Fig...., where 
$u_n$ is the rank of $x_n$ in the set ${x_1, x_2, \ldots , x_n }$, divided by $N + 1$; 
and $v_n$ is the rank of $y_n$ in the set ${y_1, y_2, \ldots , y_n }$, also divided
by $N + 1$. Here the rank of the smallest element of each sets is considered to be 1 and the rank of
the largest element is $N$. We refer to the $u_n$ and $v_n$ as normalized ranks of the $x_n$ and $y_n$. 
Ranking makes the marginal distributions uniform, isolating only the information on 
association between the variables.
